High geomagnetic field intensity recorded by anorthosite xenoliths requires a vigorous late Mesoproterozoic geodynamo

### 2022-04-03 PNAS_manuscript/Supporting Info.tex
Updates from Overleaf

>>>>

\begin{figure*}[h!]
\noindent\includegraphics[width=0.9\textwidth]{example_unmix_plot_with_data.pdf}
\centering
\caption{\footnotesize{A) Example coercivity spectra of anorthosite and diabase specimens from sites that pass or fail our paleointensity selection criteria. The specimens and fits are the same as those shown in Figure 5 in the manuscript. Data points used for fitting the coercivity curves are shown in this figure. }}
\label{fig:Cenozoic_PINT}
\end{figure*}
